\documentclass[journal,12pt,twocolumn]{IEEEtran}

\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}

\def\inputGnumericTable{}

\usepackage[latin1]{inputenc}                                 
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                        
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}
\usepackage{minibox}
\usepackage{caption} 
\usepackage{listings}
\captionsetup[table]{skip=3pt}  
\providecommand{\pr}[1]{\ensuremath{\Pr\left(#1\right)}}
\renewcommand{\thefigure}{\arabic{table}}
\renewcommand{\thetable}{\arabic{table}}
\lstset{
	%language=C,
	frame=single, 
	breaklines=true,
	columns=fullflexible
}                               


\vspace{3cm}
\title{
	AI1110: Assignment 3
}
\author{ 
	SADINENI ABHINAY - CS21BTECH11055
}	
\begin{document}
	\maketitle
	\begin{abstract}
		This document contains the solution to Question of Chapter 15 (Probability) in the NCERT Class 10 Textbook.
	\end{abstract}
	
	\textbf{Probability Excercise 15.1 Q8.}
	A bag contains 3 red balls and 5 black balls. A ball is drawn at random from the bag. What is the probability that the ball drawn is 
	\begin{enumerate}
		\item red
		\item not a red
	\end{enumerate}
	
	\textbf{Solution.}
	
	Let $X \in \{0,1\} $is random variable that denote whether the ball is red or not a red.
	Here the ball being black is considered that ball being not red because only two colours are present in the bag.
	
	\begin{table}[ht!]
	\centering
	\input{tables/table1.tex}
	\caption{Events}
	\label{table:1}
	\end{table}
	\begin{enumerate}
	\item The probability that the ball drawn is red 
	   \begin{align}
	   	\pr{X=0}&=\frac{\text{no of red colored balls}}{\text{Total no of balls}}\\
	   	        &=\frac{3}{3+5}\\
	   	        &=0.375
	   \end{align}
	\item The probability that the ball drawn is not a red, both events are mutual exculsive and exhaustive events so we can write that sum of probabilities is 1.
	\begin{align}
		\pr{X=1}&=1-\pr{X=0}\\
		&=1-\frac{3}{8}\\
		&=0.625
	\end{align}
\end{enumerate}
$\therefore$ the probability that the ball drawn is red and is not red are 0.375 and 0.675 respectively.

\end{document}